Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL

### 2015-04-17 Paper2015.tex
Modified paper to remove reference to target centre in the geometric description.

\section{Modelling}
Simulations were conducted using Geant4 version 10.0 and the binary intranuclear cascade model, as recommended in~\cite{Platt13}.
A detailed model of the ANITA geometry was implemented in Geant4, as illustrated in Fig.~\ref{fig:ANITAoverview}
Description of the geometry is given in \cite{Prokofiev2009,Prokofiev14}.
%; a summary only is given here.
%The spallation target is a tungsten cylinder of diameter \SI{5}{\cm} and length \SI{2.4}{\cm}.
%The target is cooled by water and surrounded by a stainless-steel cooling jacket.
%The target assembly with its cooling jacket appears as a small blue rectangle in Fig.~\ref{fig:ANITAoverview}.
%Lead shielding blocks in the target region are also modelled, and shown in red Fig.~\ref{fig:ANITAoverview}.
%A large electromagnet surrounding the target is modelled and shown in Fig.~\ref{fig:ANITAoverview} in grey (iron) and yellow (copper).
%An iron collimator with variable apertures is modelled  and shown downstream of the target (grey).
Except where indicated otherwise, all results in this summary are for the standard collimator size (\SI{10.2}{\cm} diameter).
In the final paper we will present results for cylindrical collimators in the range from \SIrange{3}{30}{\cm} diameter.
Simulated protons were incident axially at an energy of \SI{180}{\MeV}.
Resulting gamma and neutron fields were evaluated at several detector locations.
In this paper results are presented for three of these: the Standard User Position (SUP), \SI{2.5}{\m} downstream of the target centre~\cite{Prokofiev2009}, the Close User Position (CUP), \SI{0.75}{\m} downstream of the target, and the CUP-TOF, \SI{0.84}{m} downstream of the target.
\todo{check centre}
The SUP and CUP positions are of interest as they are positions used for SEE tests; the CUP-TOF position is the location of thin-film breakdown counter (TFBC) detectors used for beam monitoring and characterisation using time-of-flight (TOF) techniques.
Model validation will be demonstrated against CUP-TOF data (section~\ref{tbd}).

>>>>

\section{Modelling}
Simulations were conducted using Geant4 version 10.0 and the binary intranuclear cascade model, as recommended in~\cite{Platt13}.
A detailed model of the ANITA geometry was implemented in Geant4, as illustrated in Fig.~\ref{fig:ANITAoverview}
Description of the geometry is given in \cite{Prokofiev2009,Prokofiev14}.
%; a summary only is given here.
%The spallation target is a tungsten cylinder of diameter \SI{5}{\cm} and length \SI{2.4}{\cm}.
%The target is cooled by water and surrounded by a stainless-steel cooling jacket.
%The target assembly with its cooling jacket appears as a small blue rectangle in Fig.~\ref{fig:ANITAoverview}.
%Lead shielding blocks in the target region are also modelled, and shown in red Fig.~\ref{fig:ANITAoverview}.
%A large electromagnet surrounding the target is modelled and shown in Fig.~\ref{fig:ANITAoverview} in grey (iron) and yellow (copper).
%An iron collimator with variable apertures is modelled  and shown downstream of the target (grey).
Except where indicated otherwise, all results in this summary are for the standard collimator size (\SI{10.2}{\cm} diameter).
In the final paper we will present results for cylindrical collimators in the range from \SIrange{3}{30}{\cm} diameter.
Simulated protons were incident axially at an energy of \SI{180}{\MeV}.
Resulting gamma and neutron fields were evaluated at several detector locations.
In this paper results are presented for three of these: the Standard User Position (SUP), \SI{2.5}{\m} downstream of the target~\cite{Prokofiev2009}, the Close User Position (CUP), \SI{0.75}{\m} downstream of the target, and the CUP-TOF, \SI{0.84}{m} downstream of the target.
%N.B. This is downstream of the downstream edge of the target in Qian's model.
The SUP and CUP positions are of interest as they are positions used for SEE tests; the CUP-TOF position is the location of thin-film breakdown counter (TFBC) detectors used for beam monitoring and characterisation using time-of-flight (TOF) techniques.
Model validation will be demonstrated against CUP-TOF data (section~\ref{tbd}).
